### 2015-04-09 src/5_2_Proposal.tex
ordenando propuesta 2

VECM parameters are those which maximise cointegration relations in the past. However, this search is computationally expensive since the Johansen
method~\cite{johansen1995} is used, which is of order $O(n^3)$. We propose
to parallelise this search in order to get new parameters at every iteration.

@@

\section{Introduction}
Both VECM and VAR model parameters are obtained using ordinary least squares
(OLS) method \cite{golub1980}. Since OLS involves many calculations, the parameter estimation
method is computationally expensive when the number of past values and
observations increases. Moreover, obtaining cointegration vectors 
is also an expensive routine because of the use of the Johansen method.

Model effectiveness is focused on out-of-sample forecast rather than in-sample
fitting. This criterion allows our proposal AVECM prediction capability to be
expressed rather than just explaining data history.

@@

\def\rot#1{{\color{red}{#1}}}
\def\gruen#1{{\color{green}{#1}}}
\def\blau#1{{\color{blue}{#1}}}

\section{Motivation} \label{sec:proposal}

Cointegration vectors can be found applying the Johansen method which uses a
sample of the last historical data. However, one of the main limitations of this
methodology is that it assumes cointegration vectors do not change in time.
In fact, the long-run relationships between the time series might change due to
several economic factors that can lead to structural breaks in the cointegrating
relation \cite{gregoryETal1996}. 
Experiments show that cointegration depends on the amount $L$ of historical data
considered, and how many lags $p$ we use.

@@

\begin{figure}[!h]
  %\vspace{-0.8cm}
  \centering
  \includegraphics[width=\textwidth]{img/MAPEvsCoint-offset21600-p-2-freq-10s}
  \caption{MAPE versus percentage of cointegration. MAPE was obtained from 1000
  iterations considering several possible $L=[100,10000,400]$ and $p=[1,5]$.
  Best $L$ found was 8900.}
  \label{fig:cointvsmape}
\end{figure}

>>>>

@@

VECM parameters are obtained using ordinary least squares (OLS) method
\cite{golub1980}, which is computationally expensive when the number of past
values $L$ and observations $p$ increases. Moreover, obtaining cointegration
vectors is also an expensive routine because of the use of the Johansen method.

In this study we found that for some combinations of $L$ and $p$, the number of
cointegration relations is increased and this leads to better performance. We
propose to parallelise this search in order to achive faster execution times.

\section{The problem} \label{sec:proposal}

Cointegration vectors can be found applying the Johansen method which uses a
sample of the most recent historical data. However, one of the main limitations of this
methodology is that it assumes cointegration vectors do not change in time.  In
fact, the long-run relationships between the time series might change due to
several economic factors that can lead to structural breaks in the cointegrating
relation \cite{gregoryETal1996}.

In this study, we show that cointegration relations depend on the amount $L$ of
historical data considered, and how many lags $p$ were used. This search is
computationally expensive, considering that the Johansen
method~\cite{johansen1995} (which is of order $O(n^3)$) is used and these
parameters change at every iteration.

Our proposal consists on to parallelise this search in order to get new
parameters at every iteration.

@@

\section{Methodology}

The relation between the number of cointegration relations and parameters $L$
and $p$ is studied and then a relation between cointegration and performance is
stated.

@@

\begin{figure}[!h]
  %\vspace{-0.8cm}
  \centering
  \includegraphics[width=0.8\textwidth]{img/MAPEvsCoint-offset21600-p-2-freq-10s}
  \caption{MAPE versus percentage of cointegration. MAPE was obtained from 1000
  iterations considering several possible $L=[100,10000,400]$ and $p=[1,5]$.
  Best $L$ found was 8900.}
  \label{fig:cointvsmape}
\end{figure}
